Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-05-26 main.tex
:paintbrush: Update probability and block illustrations

\begin{abstract}
	Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	We introduce the concept of Metascatter, which adapts the input probability distribution of a finite-state backscatter device based on Channel State Information (CSI), to simultaneously act as parasitic source of Symbiotic Radio (SR) that conveys sensor data and reflecting element of Intelligent Reflecting Surface (IRS) that assists legacy transmission.
	Using shared spectrum, energy, and infrastructures, fully cognitive networks can be built over Metascatter, and we consider a basic scenario where a multi-antenna Access Point (AP) and multiple Metascatter simultaneously transmit to a single-antenna user.
	Since tags involve load switching and the primary and backscatter messages are multiplied (instead of superposed) in the received signal, it is assumed the user employ joint energy detection on all tags, then model their reflection pattern within the equivalent CSI for primary decoding.
	We characterize the achievable primary-(sum-)backscatter rate region through a joint optimization of transmit beamforming vector at the AP, input probability distribution at the tags, and energy detection regions at the user.
	A suboptimal solution is provided by the Block Coordinate Descent (BCD) method, where the beamforming, input distribution, and decision thresholds are obtained by Successive Convex Approximation (SCA), Karush–Kuhn–Tucker (KKT), and Dynamic Programming (DP), respectively.
	Simulation results demonstrate Metascatter can exploit the additional backscatter path to transmit and assist.
\end{abstract}

@@

\begin{section}{Backscatter Principles}
	% \begin{figure}[!t]
	% 	\centering
	% 	\resizebox{0.6\columnwidth}{!}{
	% 		\begin{circuitikz}[transform shape]
	% 			\coordinate (O) at (0,0);
	% 			\node[block,from={O to $(O) + (6.375,3.25)$}](T){};
	% 			\draw (0,1.75)
	% 			to[short] ++(-0.875,0)
	% 			to[short] ++(0,0.5) node[bareantenna](A){Bx};
	% 			\draw (0,1.75)
	% 			to[short,-*] ++(0.25,0) coordinate(J);
	% 			\draw (J)
	% 			to[short] ++(0,1)
	% 			to[short] ++(0.5,0) coordinate(J1);
	% 			\node[block,from={$(J1) + (0,-0.25)$ to $(J1) + (2.5,0.25)$}](R){Rectifier};
	% 			\draw (J)
	% 			to[short] ++(0.5,0) coordinate(J2);
	% 			\node[block,from={$(J2) + (0,-0.25)$ to $(J2) + (2.5,0.25)$}](D){Demodulator};
	% 			\draw (J)
	% 			to[short] ++(0,-1)
	% 			to[short] ++(0.5,0) coordinate(J3)
	% 			to [vR,mirror,invert,/tikz/circuitikz/bipoles/length=1cm] ++(1.75,0) node[ground,rotate=90]{};
	% 			\node[block,from={$(J3) + (0,-0.25)$ to $(J3) + (2.5,0.25)$},draw=none](M){};
	% 			\draw ($(J3) + (0,-0.25)$) rectangle ($(J3) + (2.5,0.25)$);
	% 			\draw ($(J3) + (1.25,-0.5)$) node[]{Modulator};
	% 			\draw[dashed,-{Latex[length=2mm]}] (R.east) -- ++(0.75,0);
	% 			\draw[-{Latex[length=2mm]}] (D.east) -- ++(0.75,0);
	% 			\draw[{Latex[length=2mm]}-] (M.east) -- ++(0.75,0);
	% 			\node[block,from={$(R.east) + (0.75,-0.25)$ to $(R.east) + (2.875,0.25)$}](P){Power buffer};
	% 			\node[block,from={$(M.east) + (0.75,-0.25)$ to $(D.east) + (2.875,0.25)$}](S){Digital\\section};
	% 			\draw[dashed,-{Latex[length=2mm]}] (P.south) to (S.north);
	% 			\coordinate (F1) at ($(P.south)!0.5!(S.north)$);
	% 			\coordinate (F2) at ($(D.east)!0.5!(S.west)$);
	% 			\coordinate (F3) at ($(D.south)!0.5!(M.north)$);
	% 			\draw[dashed] (F1) to (F1-|D.north);
	% 			\draw[dashed,-{Latex[length=2mm]}] (F1-|D.north) to (D.north);
	% 			\draw[dashed] (F1-|F2) to (F2|-F3) to (M|-F3);
	% 			\draw[dashed,-{Latex[length=2mm]}] (M|-F3) to (M.north);
	% 		\end{circuitikz}
	% 	}
	% 	\caption{The block diagram and equivalent circuit of a passive tag. The solid and dashed vectors represent signal and energy flows.}
	% 	\label{fi:tag_block_diagram}
	% \end{figure}

	\begin{figure}[!t]
		\centering
		\subfloat[Block diagram]{
			\resizebox{0.6\columnwidth}{!}{
				\begin{circuitikz}[transform shape]
					\coordinate (O) at (0,0);
					\node[block,from={O to $(O) + (6.375,3.25)$}](T){};
					\draw (0,1.75)
					to[short] ++(-0.875,0)
					to[short] ++(0,0.5) node[bareantenna](A){Bx};
					\draw (0,1.75)
					to[short,-*] ++(0.25,0) coordinate(J);
					\draw (J)
					to[short] ++(0,1)
					to[short] ++(0.5,0) coordinate(J1);
					\node[block,from={$(J1) + (0,-0.25)$ to $(J1) + (2.5,0.25)$}](R){Rectifier};
					\draw (J)
					to[short] ++(0.5,0) coordinate(J2);
					\node[block,from={$(J2) + (0,-0.25)$ to $(J2) + (2.5,0.25)$}](D){Demodulator};
					\draw (J)
					to[short] ++(0,-1)
					to[short] ++(0.5,0) coordinate(J3)
					to [vR,mirror,invert,/tikz/circuitikz/bipoles/length=1cm] ++(1.75,0) node[ground,rotate=90]{};
					\node[block,from={$(J3) + (0,-0.25)$ to $(J3) + (2.5,0.25)$},draw=none](M){};
					\draw ($(J3) + (0,-0.25)$) rectangle ($(J3) + (2.5,0.25)$);
					\draw ($(J3) + (1.25,-0.5)$) node[]{Modulator};
					\draw[dashed,-{Latex[length=2mm]}] (R.east) -- ++(0.75,0);
					\draw[-{Latex[length=2mm]}] (D.east) -- ++(0.75,0);
					\draw[{Latex[length=2mm]}-] (M.east) -- ++(0.75,0);
					\node[block,from={$(R.east) + (0.75,-0.25)$ to $(R.east) + (2.875,0.25)$}](P){Power buffer};
					\node[block,from={$(M.east) + (0.75,-0.25)$ to $(D.east) + (2.875,0.25)$}](S){Digital\\section};
					\draw[dashed,-{Latex[length=2mm]}] (P.south) to (S.north);
					\coordinate (F1) at ($(P.south)!0.5!(S.north)$);
					\coordinate (F2) at ($(D.east)!0.5!(S.west)$);
					\coordinate (F3) at ($(D.south)!0.5!(M.north)$);
					\draw[dashed] (F1) to (F1-|D.north);
					\draw[dashed,-{Latex[length=2mm]}] (F1-|D.north) to (D.north);
					\draw[dashed] (F1-|F2) to (F2|-F3) to (M|-F3);
					\draw[dashed,-{Latex[length=2mm]}] (M|-F3) to (M.north);
				\end{circuitikz}
			}
			\label{fi:block_diagram}
		}
		\setcounter{subfigure}{2}%
		\subfloat[Scatter model]{
			\resizebox{0.35\columnwidth}{!}{
				\begin{circuitikz}[transform shape]
					\tikzstyle{every node}=[font=\Large]
					\draw (0,0) node[bareantenna](bareantenna){};
					\draw (bareantenna.west) ++(-1.5,0) node[waves](WI){};
					\draw (WI.north east) ++(0.25,0) node[font=\Large]{$\vec{E}_{\mathrm{I}}$};
					\draw (WI.south east) ++(0.25,0) node[font=\Large]{$\vec{H}_{\mathrm{I}}$};
					\draw (bareantenna.east) ++(0.875,0) node[waves](WR){};
					\draw (WR.north east) ++(0.35,0) node[font=\Large]{$\vec{E}_m$};
					\draw (WR.south east) ++(0.35,0) node[font=\Large]{$\vec{H}_m$};
					\draw (bareantenna)
					to [R=$Z_{\mathrm{A}}$] ++(0,-1.5) node[rotary switch=4 in 90 wiper 30,anchor=ext center,rotate=270](SW){};
					\draw (SW.cout 2) node[below=0.1cm,font=\Large]{$m$}
					to [R=$Z_m$] ++(2,0) node[ground]{};
				\end{circuitikz}
			}
			\label{fi:scatter_model}
		}
		\setcounter{subfigure}{1}
		\subfloat[Equivalent circuit]{
			\resizebox{0.9\columnwidth}{!}{
				\begin{circuitikz}[transform shape]
					\tikzstyle{every node}=[font=\Large]
					\draw (0,0) coordinate(O)
					to [sV,l=$V_0$] ++(0,1.5)
					to [L,l=$X_{\mathrm{A}}$] ++(0,1.5)
					to [R=$R_{\mathrm{A}}$,-*] ++(3,0) coordinate(AM)
					to [sI,l_=$I_0$,-*] ++(0,-3)
					to [short] (O);
					\draw (AM)
					to [short] ++(0.5,0)
					to [L,l=$X_m$,-*] ++(3,0) coordinate(M)
					to [R=$R_m^{\mathrm{S}}$] ++(3,0) coordinate(MH);
					\draw (M)
					to [R=$R_m^{\mathrm{P}}$,-*] ++(0,-3);
					\draw (MH)
					to [D,-*] ++(1.5,0) coordinate(H)
					to [C=$X_{\mathrm{H}}$,-*] ++(0,-3);
					\draw (H)
					to [short] ++(1.5,0)
					to [R=$R_{\mathrm{H}}$] ++(0,-3)
					to [short] (O);

					\draw [blue,dashed] (-1.125,-0.5) rectangle (3.5,4);
					\draw [yellow,dashed] (4,-0.5) rectangle (9,4);
					\draw [red,dashed] (9.5,-0.5) rectangle (13.5,4);

					\draw [blue] (1.125,4.25) node[]{Antenna};
					\draw [yellow] (6.5,4.25) node[]{Modulator};
					\draw [red] (11.5,4.25) node[]{Harvester + Chip};

					\draw (3.375,2.675) to [short] (3.375,3.175) to [short] (3.25,3.175) to [short,i_=$Z_{\mathrm{A}}$] (3.125,3.175);
					\draw (4.125,-0.125) to [short] (4.125,0.375) to [short] (4.25,0.375) to [short,i=$Z_m$] (4.375,0.375);
					\draw (9.625,-0.125) to [short] (9.625,0.375) to [short] (9.75,0.375) to [short,i=$Z_{\mathrm{H}}$] (9.875,0.375);
				\end{circuitikz}
			}
			\label{fi:equivalent_circuit}
		}
		\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	\end{figure}
	% In a bistatic backscatter system,
	% Consider a bistatic backscatter system with an excitation source, multiple passive tags, and a backscatter reader.
	Passive backscatter devices (a.k.a., tags) harvest energy from and modulate information over surrounding \gls{rf} signal.
	As shown in Fig. \subref*{fi:block_diagram}, a typical passive tag consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}. Its equivalent circuit is also given by Fig. \subref*{fi:equivalent_circuit}.
	When illuminated, the tag absorbs a portion of the impinging wave and scatters the rest back to the space.
	The absorbed signal can be used for source decoding and energy harvesting \cite{Kim2021a}, while the scattered signal can be decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
	The structural mode scattering applies to general objects and is related to the antenna structure, shape and material, which contributes to environment multipath and can be covered by channel estimation \cite{Boyer2014}.
	On the other hand, the antenna mode scattering models the antenna radiation and depends on the antenna-load impedance mismatch, which can be used for backscatter modulation \cite{Boyer2012} or channel reconfiguration \cite{Wu2021b}.
	Fig. \subref*{fi:scatter_model} illustrates the scatter model.
	For a tag with $M$ candidate states, the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as
	\begin{footnote}
		It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.
	\end{footnote}
	\begin{equation}
		\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
		\label{eq:reflection_coefficient}
	\end{equation}
	where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.

@@

>>>>

\begin{abstract}
	Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	We uniquely introduce the concept of Metascatter, which adapts the input probability distribution of a finite-state backscatter device based on Channel State Information (CSI), to simultaneously act as parasitic source of Symbiotic Radio (SR) that conveys sensor data, and reflecting element of Intelligent Reflecting Surface (IRS) that assists legacy transmission.
	Using shared spectrum, energy, and infrastructures, fully cognitive networks can be built over Metascatter, and we consider a fundamental scenario where a multi-antenna Access Point (AP) and multiple Metascatter simultaneously transmit to a single-antenna user.
	Since tags involve load switching and the primary and backscatter messages are multiplied (instead of superposed) in the received signal, it is assumed the user employ joint energy detection on all tags, then model their reflection pattern within the equivalent CSI for primary decoding.
	We characterize the achievable primary-(sum-)backscatter rate region through a joint optimization of transmit beamforming vector at the AP, input probability distribution at the tags, and energy detection regions at the user.
	A suboptimal solution is provided by the Block Coordinate Descent (BCD) method, where the beamforming, input distribution, and decision thresholds are obtained by Successive Convex Approximation (SCA), Karush–Kuhn–Tucker (KKT), and Dynamic Programming (DP), respectively.
	Simulation results demonstrate Metascatter can exploit the additional backscatter path to transmit and assist.
\end{abstract}

@@

\begin{section}{Backscatter Principles}
	\begin{figure}[!t]
		\centering
		\subfloat[Block Diagram]{
			\resizebox{0.6\columnwidth}{!}{
				\input{assets/block_diagram.tex}
			}
			\label{fi:block_diagram}
		}
		\setcounter{subfigure}{2}%
		\subfloat[Scatter Model]{
			\resizebox{0.35\columnwidth}{!}{
				\input{assets/scatter_model.tex}
			}
			\label{fi:scatter_model}
		}
		\setcounter{subfigure}{1}
		\subfloat[Equivalent Circuit]{
			\resizebox{0.95\columnwidth}{!}{
				\input{assets/equivalent_circuit.tex}
			}
			\label{fi:equivalent_circuit}
		}
		\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	\end{figure}
	% In a bistatic backscatter system,
	% Consider a bistatic backscatter system with an excitation source, multiple passive tags, and a backscatter reader.
	Passive backscatter devices (a.k.a., tags) harvest energy from and modulate information over surrounding \gls{rf} signal.
	As shown in Fig. \subref*{fi:block_diagram}, a typical passive tag consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}. Its equivalent circuit is also given by Fig. \subref*{fi:equivalent_circuit}.
	When illuminated, the tag absorbs a portion of the impinging wave and scatters the rest back to the space.
	The absorbed signal can be used for source decoding and energy harvesting \cite{Kim2021a}, while the scattered signal can be decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
	The structural mode scattering applies to general objects and is related to the antenna structure, shape and material, which contributes to environment multipath and can be covered by channel estimation \cite{Boyer2014}.
	On the other hand, the antenna mode scattering models the antenna radiation and depends on the antenna-load impedance mismatch, which can be used for backscatter modulation \cite{Boyer2012} or channel reconfiguration \cite{Wu2021b}.
	Fig. \subref*{fi:scatter_model} illustrates the scatter model.
	For a tag with $M$ candidate states, the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as
	\begin{footnote}
		It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.
	\end{footnote}
	\begin{equation}
		\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
		\label{eq:reflection_coefficient}
	\end{equation}
	where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.

@@

		\begin{figure}[!t]
			\centering
			\subfloat[Reflection State Distribution]{
				\resizebox{0.95\columnwidth}{!}{
					\input{assets/reflection_state_distribution.tex}
				}
			}
			\\
			\subfloat[Time Block Structure]{
				\resizebox{0.95\columnwidth}{!}{
					\input{assets/time_block_structure.tex}
				}
			}
			\caption{Reflection state distribution and time block structure of \gls{sr}, \gls{irs}, and Metascatter. $T_s$ and $T_c$ denote the primary and backscatter symbol length, respectively. Based on \gls{csi}, Metascatter adapts the reflection state distribution to unify data transmission and channel reconfiguration.}
		\end{figure}
